Data_visualization

### 2018-08-03 Rmd/Data_visualization.Rmd
last changes

---
title: "Data_visualization"
output:
      pdf_document
---

@@

\newpage

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',out.width='55%'}
#Preparing seed set plots, starting with Petunia

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
par(mfrow=c(2,3))

#read data and cleaning
pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
#removing samples where seeds got lost, first ones of the experiment
pein_seed_set <- pein_seed_set[-c(42,47,49),]

p <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

#Different colour per family
p <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

#Different colour per family
p <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

#Different colour per family
p <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

#
##
###
#B. OLERACEA
###
##
#

#Different colour per family
p <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

#Different colour per family
p <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

#Different colour per family
p <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
#
##
###
#S. ALBA  
###
##
#

#Different colour per family
p <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)

```
\newpage
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5),plot.margin=unit(c(1,1,-0.5,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5),plot.margin=unit(c(1,1,-0.5,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5), plot.margin=unit(c(-0.5,1,1,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5), plot.margin=unit(c(-0.5,1,1,1),"cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

grid.arrange(lg[[1]], lg[[2]], lg[[3]], lg[[4]], nrow=2,ncol=2)

>>>>

---
title: "Data_visualization"
output:
      pdf_document
---
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

grobz <- lapply(list(a, b, c, d), ggplotGrob)
grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
                           ncol = 2, top="Solanaceae Focal Species")

grid.draw(grobz.plot)

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
library(dplyr)

#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)
##
###
#B. OLERACEA
###
##
#

#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
#
##
###
#S. ALBA  
###
##
#

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")

grobz <- lapply(list(a, b, c, d), ggplotGrob)
grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")), ncol = 2,top="Brassicaceae Focal species")

grid.draw(grobz.plot)

@@
